### 2020-11-11 Thesis-Chapter2-Background.tex
Write EA and alternatives section
Begin threat model chapter
Progress on threat model

\mytab{table:security-and-crypto} connects each security property to its cryptographic basis. While lacking direct
cryptographic foundations, availability indirectly relies on each other property, and authorization schemes are
typically rooted in authentication.

% Spoofing                  Authentication
% Tampering                 Integrity
% Repudiation               Non-Repudiation
% Information Disclosure    Confidentiality
% Denial of Service         Availability
% Elevation of Privilege    Authorization
\begin{table}[h]
    \caption[Security Properties and Cryptography]{The Cryptographic Basis of Security Properties}
    \label{table:security-and-crypto}
    \centering
    \begin{tabular}{|l|l|}
        \hline
        \thead{Property} & \thead{Cryptographic Basis} \\ \hline
        Authentication  & Digital certificates \\ \hline
        Integrity       & Cryptographic hashes \\ \hline
        Non-repudiation & Digital signatures \\ \hline
        Confidentiality & Encryption \\ \hline
        Availability    & \small{\ii{based on architecture}} \\ \hline
        Authorization   & \small{\ii{rooted in authentication}} \\ \hline
    \end{tabular}
\end{table}

@@

\subsection{Alternative Approaches}

@@

\Acp{DFD} are one tool designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and
external entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data
flow, not control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is
the primary concern. \myfig{fig-dfd-demo} shows the basic elements of a \ac{DFD}. In \mychap{chap-threatmodel} I create
\acp{DFD} in this style to analyze the threats already present and those that \ac{EA} would introduce.

>>>>

\mytab{table-security-and-crypto} connects each security property to its cryptographic basis. While lacking direct
cryptographic foundations, availability indirectly relies on each other property, and authorization schemes are
typically rooted in authentication.

% Spoofing                  Authentication
% Tampering                 Integrity
% Repudiation               Non-Repudiation
% Information Disclosure    Confidentiality
% Denial of Service         Availability
% Elevation of Privilege    Authorization
\begin{table}[h]
    \caption{The Cryptographic Basis of Security Properties}
    \label{table-security-and-crypto}
    \centering
    \begin{tabular}{ |l|l| }
        \hline
        \thead{Property} & \thead{Cryptographic Basis} \\ \hline
        Authentication  & Digital certificates \\ \hline
        Integrity       & Cryptographic hashes \\ \hline
        Non-repudiation & Digital signatures \\ \hline
        Confidentiality & Encryption \\ \hline
        Availability    & \small{\ii{based on architecture}} \\ \hline
        Authorization   & \small{\ii{rooted in authentication}} \\ \hline
    \end{tabular}
\end{table}

@@

\subsection{Alternative Approaches}
\label{sec-alt-approaches}

@@

\Acp{DFD} are one tool designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and
external entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data
flow, not control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is of
primary concern. \myfig{fig-dfd-demo} shows the basic elements of a \ac{DFD}. In \mychap{chap-threatmodel} I create
\acp{DFD} in this style to analyze the threats already present and those that \ac{EA} would introduce.

### 2020-11-11 Thesis-Chapter5-ThreatModel.tex
Progress on threat model

\ldawmsr introduces device key escrow and an unexposed hardware interface that mediates \ac{EA} requests. When prompted,
the hardware interface produces a Device ID. The law enforcement officer (assuming proper circumstances) receives this
Device ID and reports it to her agency. The agency signs a request including the Device ID and presents it to the
vendor's access compliance department. The vendor authenticates the request, audits the corresponding legal documents,
and looks up the corresponding Device Seal key. This key is encrypted using the same agency's public key and returned to
the agency. The agency decrypts the Device Seal key and issues it to the agent, who enters it through the special
interface. The Secure Enclave Processor uses the private Device Seal key to decrypt the Class key, which was saved in
key storage encrypted by the device's public Device Seal key, and the unlock process proceeds as normal from there. Each
of these steps is analyzed in closer detail.

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.81\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR.png}
    \caption{The LDAWMSR data flow diagram.}
    \label{fig-dfd-ldawmsr}
\end{figure}

\section{Discussion of Threats}

@@

@@

>>>>

\ldawmsr introduces device key escrow, an unexposed hardware interface that mediates \ac{EA} requests, and a vendor
mediated authorization process. To achieve its goals, the proposal relies on the concepts of self-escrow, time vaulting,
authorization, and transparency. These concepts are summarized in \mytab{table-ldawmsr-concepts}; see the original paper
for full detail \cite{savage_lawful_2018}.

\begin{table}[h]
  \caption{Central Concepts in the \ldawmsr Proposal}
  \label{table-ldawmsr-concepts}
  \begin{FlushLeft}
    \begin{tabular}{ |l|p{6.3cm}|p{6.3cm}| }
      \hline
      \thead{Concept} & \thead{Implementation} & \thead{Outcome} \\ \hline
      Self-escrow
      & The Class key is escrowed in the device's Secure Enclave (or equivalent) using a write-only component; i.e.,
        software can update the key, but only an unexposed hardware interface can read it.
      & Since the Class key itself is being stored, there is no change to the security of the underlying cryptographic
        protocols. Physical possession and partial disassembly is required, which introduces practical barriers to mass
        surveillance.
      \\ \hline
      Time vaulting
      & The hardware interface responds to requests only after proof of sustained possession for a ``lockup period
        (e.g., 72 hours).''
      & The waiting period precludes ``sneak and peak'' attacks and further reduces the utility for mass surveillance.
      \\ \hline
      Authorization
      & After the lockup period, the requestor must provide evidence of authorization. This comes from a shared secret
        between the device and the manufacturer which can be obtained via legal process.
        % Vendor authorization escrow (as opposed to _key_ escrow)
      & Physical possession is now not enough; law enforcement (or attackers) must provide this secret information to
        the device to unlock it.
      \\ \hline
      Transparency
      & In addition to the device disassembly, the escrow agent modifies the device (e.g., burns a fuse) when it has
        been unlocked. The device firmware detects this modification.
      & The device user has evidence that the device has been unlocked, preventing covert usage.
      \\ \hline
    \end{tabular}
  \end{FlushLeft}
\end{table}

Device key escrow is considered the most promising technical \ac{EA} direction because of the unique capabilities that
secure hardware offers, and \ldawmsr demonstrates this capabilities perfectly. The greatest of these capabilities are
physical possession requirements and strong transparency. Physical possession requirements strongly mitigate mass
surveillance and, as Savage puts it, ``provides a more intuitive compatibility with common under-standings of the
government’s reasonable law enforcement powers (e.g., the ability to seize physical property under court order) than
more information-centric approaches, which may appear covert by comparison'' \cite{savage_lawful_2018}. Transparency is
also rooted in the physicality of the approach, wherein the device cannot be unlocked without making irreversible and
detectable changes, mitigating both mass surveillance and common criminal abuse.

One clear weakness in the design is the shared secret between the device and the manufacturer used in the authorization
protocol. The key may be stored on the device, but one can access it if they have this shared secret. This is very much
like trusted-party key escrow where the vendor is the trusted party, only they store the authentication key instead of
the unlock key itself. Due to this similarity, one of the biggest \ac{EA} problems of centralized risk is not fully
addressed. This is discussed further in \mysec{sec-prop-threats}.

\ldawmsR's full data flow is illustrated in \myfig{fig-dfd-ldawmsr}. The proposal offers a few variations of the
self-escrow and authorization protocols. This figure uses the asymmetric key pair approach for Class key encryption in
the Secure Enclave, which has stricter hardware requirements; however, Savage offers a symmetric key variant that
achieves the same purposes. The asymmetric key pair approach was chosen here because it is semantically clearer and
easier to illustrate.

\begin{figure}[p]
    \centering\CaptionFontSize
    \includegraphics[width=0.9\linewidth]{dfds/build/DAR-level-1-crypto-iphone-LDAMSR.png}
    \caption{The LDAWMSR data flow diagram.}
    \label{fig-dfd-ldawmsr}
\end{figure}

The lawful access use case operates as follows: law enforcement obtains a warrant to conduct a search, including the
suspect's mobile device. They obtain the phone, disassemble it to expose the \ac{EA} hardware interface, and begin the
time-vaulted access request. After the lockout period is completed, the device offers its Device ID only. The law
enforcement agency's digital forensics department digitally signs the Device ID and sends it to the device vendor,
alongside the warrant and accompanying proof of legal authorization. The vendor's access compliance department audits
the legal documents and submits the digitally signed Device ID to a secure computing environment such as a Hardware
Security Module. The secure environment authenticates the digital signature, looks up the device's private Device Seal
Key and authorization value, and encrypts them with the law enforcement agency's public key. These encrypted artifacts
are returned to the agency, which decrypts and submits them to the device through the dedicated interface. First is
the authorization value, which is hashed and compared to the stored hash. If that values match, the device accepts and
uses the private Device Seal Key to decrypt the Class key, which was escrowed after being encrypted but the public
Device Seal Key. Once the Class key is decrypted, the escrow agent burns a fuse, and the device is unlocked for forensic
investigation.

\section{Discussion of Threats}
\label{sec-prop-threats}

% Full lifecycle--how do the keys get in the DB!

The proposal has been illustrated. What threats does it introduce? Recall from \mysec{sec-crypto-basics} that security
can be expressed in the properties of authentication, integrity, non-repudiation, confidentiality, availability, and
authorization. Threats are often expressed as the negative of these properties: spoofing, tampering, repudiation,
information disclosure, denial of service, and elevation of privileged \cite{shostack_threat_2014}. This section
analyzes \ldawmsr using these categories.

\subsection{Spoofing}

\begin{table}[h]
  \caption{Spoofing Threats}
  \label{table-ldawmsr-concepts}
  \begin{FlushLeft}
    \begin{tabular}{ |l|p{2cm}|p{2cm}|p{4.8cm}|p{4.8cm}| }
      \hline
      \thead{ID} & \thead{Identity \\ Spoofed} & \thead{With \\ Respect To} & \thead{Effect} & \thead{Mitigation}
      \\ \hline
      S1 & Device & Officer
      & Planted device to unlock unauthorized device.
      & Require it to be in the forensics department itself.
      \\ \hline
    \end{tabular}
  \end{FlushLeft}
\end{table}

\ii{S1} is Eran Tromer's attack on CLEAR.

\subsection{Tampering}

\subsection{Repudiation}

\subsection{Information Disclosure}

\subsection{Denial of Service}

\subsection{Elevation of Privilege}

@@

% Or just, relationship to my goals?

@@

% Reflection on how much progress this represents
